Benchmarking on Rigetti architecture

### 2022-09-29 txt/manuscript.tex
Last part of section 2 rewritten.

Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
the field $\mathbb{C}$. For  simplicity notation, square matrices will be 
denoted by
$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$ 
will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite 
matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is 
positive semidefinite operators having
trace equal to one, will be denoted $\Omega_d$.  The subset of $M_d$ consisting of 
unitary matrices will be denoted by
$\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
$\DD \UU_d$.  We will also need a linear
mapping transforming $M_{d_1}$ into $M_{d_2}$, which will be denoted \begin{equation}
\Phi: M_{d_1 } \rightarrow M_{d_2}.
\end{equation} 
There
exists a bijection between introduced linear mappings $\Phi$ and set of matrices $M_{d_1d_2}$,  known as the Choi-
Jamio{\l}kowski isomorphism.

@@

\subsubsection{Diamond norm}
This section defines a special norm on the space of linear mappings, known as the diamond norm,
and establishes some of its properties. 
Next, we will also explain the precise connection between the diamond
norm and the task of quantum operations discrimination.

@@

In case then 
we consider the discrimination setup between two von Neumann 
measurements $\PP_U$ and $\PP_\Id$, $U\in \UU_d$ we obtain that (from Theorem 1 \cite{puchala2018strategies})
\begin{equation}
\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond,
\end{equation}
where $\Phi_U$ is unitary channel and 
$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$.

@@

Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
Assume that the unitary matrix $U$ is of the form 
\begin{equation}
U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
\end{equation}
where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
In this section we present theoretical probability of correct 
discrimination between these measurements. Moreover, we create the optimal theoretical strategy of their discriminate. 
Such a probability can be calculated using Holevo-Helstrom theorem and 
Theorem 1 from~\cite{puchala2018strategies}. 
This probability will be calculated in 
subsection~\ref{sec:example_theoretical_probability}. Later, we will 
discuss the realization of this scheme in 
subsection~\ref{sec:example_realization}. For such realization, we 
will need the proper input state, (see sec.~\ref{sec:example_discriminator}) 
and final measurement (see sec.~\ref{sec_example_final_measurement}).

\subsection{Theoretical probability}\label{sec:example_theoretical_probability}
In this section we calculate the theoretical probability of correct discrimination between two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H \diag(1, e^{i \phi}) H^\dagger$, where  $\phi \in [0, 2\pi)$. To do that, we will present an auxiliary lemma.   
\begin{lemma}\label{lemma:min-e-optimal}
	Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
	$\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
	\begin{equation}
	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
	\Phi_\Id\|_\diamond,
	\end{equation}

>>>>

Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is
positive semidefinite operators having trace equal to one, will be denoted
$\Omega_d$.  The subset of $M_d$ consisting of unitary matrices will be denoted
by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
$\DD \UU_d$.  We will also need a linear mapping transforming $M_{d_1}$ into
$M_{d_2}$, which will be denoted 
\begin{equation}
\Phi: M_{d_1 } \rightarrow M_{d_2}.
\end{equation} 
There
exists a bijection between introduced linear mappings $\Phi$ and set of matrices $M_{d_1d_2}$,  known as the Choi-
Jamio{\l}kowski isomorphism.

@@

\subsubsection{Diamond norm}
This section defines a special norm on the space of linear mappings, known as 
the diamond norm, and establishes some of its properties. 
Next, we will explain the precise connection between the diamond
norm and the task of quantum operation discrimination.

@@

In the case of discrimination between two von Neumann measurements $\PP_U$ and 
$\PP_\Id$ we know that (from Theorem 1 \cite{puchala2018strategies})
\begin{equation}
\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond,
\end{equation}
where $\Phi_U$ is unitary channel and $\diaguni_d$ be the set of diagonal 
unitary matrices of dimension $d$.

@@

Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
Assume that the unitary matrix $U$ is of the form 
\begin{equation}
U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
\end{equation}
where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
In this section we present theoretical probability of correct 
discrimination between these measurements. Moreover, we create the optimal 
theoretical strategy of their discrimination. 
Such a probability can be calculated using Holevo-Helstrom theorem and 
Theorem 1 from~\cite{puchala2018strategies}. 
This probability will be calculated in 
subsection~\ref{sec:example_theoretical_probability}. Later, we will 
discuss the realization of this scheme in 
subsection~\ref{sec:example_realization}. For such realization, we 
will need the proper input state, (see sec.~\ref{sec:example_discriminator}) 
and final measurement (see sec.~\ref{sec_example_final_measurement}).

\subsection{Theoretical probability}\label{sec:example_theoretical_probability}
In this section we calculate the theoretical probability of correct discrimination between two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H \diag(1, e^{i \phi}) H^\dagger$, where  $\phi \in [0, 2\pi)$. To do that, we will present an auxiliary lemma.   
\begin{lemma}\label{lemma:min-e-optimal}
Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then 
